Finite element analysis ofmulti-dimensional and simplifiedmodels for beams and plates

### 2023-11-26 files/Chapter3/dynamicconvergence.tex
Chapter 3

\textcolor{red}{***************** NEW ********************************}

\subsubsection{*** Example of the Galerkin approximation of a cantilever Timoshenko beam ***}
Consider the example of the cantilever Timoshenko beam model from Section \ref{sec:existence}. In this section the variational problem Problem T-2V is given in terms of bilinear forms.

@@

Consider a a set of $n+1$ linear independent, piecewise linear basis functions $\delta_i \in T[0,1]$. The subset of these functions that satisfies the boundary conditions are called admissible basis functions. For Problem 2-T, the admissible basis functions are ${\delta_i}$ for $i = 1,2,...,n$. Define the space $S^h$ as the space spanned by the admissible basis functions, i.e.
\begin{eqnarray*}
	S^h = \textrm{span}\{\delta_1, \delta_2, ..., \delta_n\}.
\end{eqnarray*}

This space $S^h$ is a finite dimensional subspace of $T[0,1]$. Define the following functions $w^h \in S^h$ and $\phi^h \in S^h$ as
\begin{eqnarray*}
	w^h(t) & = & \sum_{i=1}^{n} w(x_i^*,t) \delta_i(t),\\
	\phi^h(t) & = & \sum_{i=1}^{n} w(x_i^*,t) \delta_i(t),
\end{eqnarray*} where $x^*_i \in [x_i, x_{i+1}]$.

Using these functions, the Galerkin approximation for Problem T-2, referred to as Problem T-2G, can be derived.

\subsubsection{Problem T-2G}
Find a function $u_h \in S^h$ such that for all $t \in [0,1]$,
\begin{eqnarray*}
	c(u''_h(t),v) + b(u_h(t),v) & = & (Q^I(t),v),
\end{eqnarray*} for each $v \in S^h$, where $u_h = \langle w^h, \phi^h \rangle$. $Q^I$ is a vector of the values of $Q(x^*_i)$ for $i = 0,1,2,...,n$.

@@

\textcolor{red}{***************** NEW ********************************}

>>>>

Consider the example of the cantilever Timoshenko beam model from Section \ref{sec:existence}. In this section the variational problem Problem T-2V is given in terms of bilinear forms.

@@

Consider a set of $n+1$ linear independent, piecewise linear basis functions $\delta_i$. The subset of these functions that satisfies the boundary conditions are called admissible basis functions. For Problem 2-T, the admissible basis functions are ${\delta_i}$ for $i = 1,2,...,n$. Define the space $S^h$ as the space spanned by the admissible basis functions, i.e.
\begin{eqnarray*}
	S^h = \textrm{span}\{\delta_1, \delta_2, ..., \delta_n\}.
\end{eqnarray*}

This space $S^h\times S^h$ is a finite dimensional subspace of $T[0,1]$. Define the following functions $w^h \in S^h$ and $\phi^h \in S^h$ as
\begin{eqnarray*}
	w^h(t) & = & \sum_{i=1}^{n} w(x_i^*,t) \delta_i(t),\\
	\phi^h(t) & = & \sum_{i=1}^{n} w(x_i^*,t) \delta_i(t),
\end{eqnarray*} where $x^*_i \in [x_i, x_{i+1}]$. Then let $u_h = (w^h, \phi^h )$.

Using these functions, the Galerkin approximation for Problem T-2, referred to as Problem T-2V$^h$, can be derived.

\subsubsection{Problem T-2V$^h$}
Find a function $u_h \in S^h\times S^h$ such that for all $t \in [0,1]$,
\begin{eqnarray*}
	c(u''_h(t),v) + b(u_h(t),v) & = & (Q^I(t),v),
\end{eqnarray*} for each $v \in S^h\times S^h$, where $u_h = ( w^h, \phi^h )$. $Q^I$ is a vector with elements $Q(x^*_i)$ for $i = 0,1,2,...,n$.

@@
